%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Yu-Siou Lin} \\[7.5pt]
\href{https://github.com/ericlinqq}{\raisebox{-0.05\height}\faGithub\ ericlinqq} \ $|$ \ 
\href{https://www.linkedin.com/in/yu-siou-lin-7a3b00252/}{\raisebox{-0.05\height}\faLinkedin\ Yu-Siou Lin} \ $|$ \ 
\href{mailto:ericlin66.cs11@nycu.edu.tw}{\raisebox{-0.05\height}\faEnvelope \ ericlin66.cs11@nycu.edu.tw} \ $|$ \ 
\href{tel:+886975108201}{\raisebox{-0.05\height}\faMobile \ +886.975.108.201} \\
\end{tabularx}



%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
% \section{Summary}
Master's student in Data Science with a deep focus on low-level systems programming. Demonstrated expertise in OS kernel development, bare-metal programming on ARM platforms, and performance optimization of Linux kernel modules. Seeking a challenging firmware or systems software engineering role.

%Experience
% \section{Experience}
% 
% \begin{jobshort}{Teaching Assistant}{Feb 2024 - June 2024}
%   Algorithms [CSIC30072], National Yang-Ming Chiao-Tung University  
% \end{jobshort}

% \begin{joblong}{Teaching Assistatnt}{Feb 2024 - June 2024}
%   \item National Yang-Ming Chiao-Tung University
%   \item Algorithm [CSIC30072]
% \end{joblong}

%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Bare Metal Operating System on RaspberryPi 3b+} & \hfill \href{https://github.com/ericlinqq/osc2024}{GitHub}\\[3.75pt]
Skills: C, ARM Assembly, Bare Metal, OS Kernel Development \\
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
      \item  \textbf{Objective:} To \textbf{master fundamental operating systems concepts} by designing, building, and deploying a functional monolithic kernel from scratch, focusing on memory management and process scheduling.
      \item \textbf{Key Achievements:}
      \begin{itemize}
        \item Engineered a complete \textbf{memory management subsystem}, featuring \textbf{buddy system page allocator} and \textbf{slab allocators}, which successfully managed efficient dynamic memory allocation for kernel objects with \texttt{less fragmentation}.
        \item Implemented a comprehensive interrupt handling mechanism, including IRQs for \textbf{hardware timers} and \textbf{UART}, enabling \textbf{asynchronous I/O} and \textbf{concurrent I/O device handling}.
        \item Implemented a robust \textbf{virtual memory system} with \textbf{demand paging} and \textbf{copy-on-write}, reducing the memory footprint and time of forked processes.
        \item Developed a \texttt{preemptive}, \texttt{priority-based} \textbf{round-robin scheduler} that managed multiple \textbf{concurrent} user-level tasks and handled \textbf{POSIX signals}.
      \end{itemize}
    \item \textbf{Outcome:} Successfully \textbf{deployed the OS on Raspberry Pi 3B+ hardware}, achieving a stable runtime environment capable of \textbf{loading and executing user-space programs}, with a custom shell interface.    
    \end{itemize}
}  \\

\textbf{Linux Kernel Module: Fibonacci Driver using Big Integer Arithmetic} & \hfill \href{https://github.com/ericlinqq/fibdrv}{GitHub} \href{https://hackmd.io/@ericlinqq/ByrjW8_ogl}{HackMD}\\[3.75pt]
Skills: C, Linux Kernel Programming, ARMv8-A, perf\_events \\
\multicolumn{2}{@{}X@{}}{
    \begin{itemize}
      \item \textbf{Objective:} To \textbf{understand Linux kernel module operations} by developing a high-throughput Fibonacci driver capable of correctly calculating large numbers beyond standard integer limits, and to \textbf{investigate kernel performance overhead} through systematic benchmarking.
      \item \textbf{Key Achievements:}
      \begin{itemize}
        \item Implemented a \textbf{Fast Doubling algorithm} with a \textbf{custom arbitrary-precision big-integer} library, accelerating computation by \textbf{4x up} compared to standard iterative methods.
      \item \textbf{Reduced performance measurement noise} through strategic kernel parameter tuning (\texttt{isolcpus}, \texttt{nohz\_full}), enabling more accurate analysis of CPU cycles.
      \item Integrated the \textbf{Performance Monitoring Unit (PMU)} via \textbf{perf\_events} for high-precision CPU cycle counting, after initial analysis showed the \texttt{Armv8-A generic timer} lacked sufficient resolution for fine-grained measurements.
      \item Diagnosed and quantified a \textbf{300\% latency increase} in \textbf{kmalloc} operations caused by \textbf{cold-cache penalties}, providing insights into kernel memory allocation behavior.
      \end{itemize}
    \item \textbf{Outcome:} The project resulted in a driver capable of efficiently computing up to at least the \textbf{100,000th Fibonacci number}. A comprehensive \textbf{technical analysis} detailing the optimization process was published on HackMD.    
  \end{itemize}
}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
\textbf{2023 - 2025} & Master's degree at \textbf{National Yang-Ming Chiao-Tung University} \\%\hfill \normalsize (GPA: 4.0/4.0) \\
\multicolumn{2}{@{}X@{}}{Institute of Data Science and Engineering (Medical Image Processing Lab, MIPLab)}  \\[3.75pt]

\textbf{2017 - 2021} & Bachelor's degree at \textbf{National Yang-Ming Chiao-Tung University} \\%\hfill \normalsize (GPA: 4.0/4.0) \\
\multicolumn{2}{@{}X@{}}{Department of Transportation and Logistics Management}  \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
%   ACTIVITIES
%----------------------------------------------------------------------------------------
\section{Activities}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
  \item \textbf{Teaching Assistant (Algorithms [CSIC30072]):} 
  \begin{itemize}
    \item Assisted the professor with overall course management and instruction for undergraduate students.
    \item \textbf{Managed course materials}, including preparing and uploading lecture videos, slides and homework assignments.
    \item \textbf{Graded homework and examinations}, providing timely and constructive feedback to students.
    \item Provided academic support by \textbf{answering student inquiries}, clarifying algorithmic concepts, and holding regular office hours.
  \end{itemize}

  \item \textbf{Operational Support (MIPLab):} 
  \begin{itemize}
    \item Assumed responsibility for \textbf{managing lab finances}, ensuring smooth operational support for the entire lab.

    \item Coordinated with professors on budget planning and allocation.

    \item Liaised with vendors for procurement and managed purchasing processes.

    \item Worked with the university's cashier division to process reimbursements and ensure financial compliance.
  \end{itemize}

  \item \textbf{Dance Troupe Member \& Camp Counselor (NYCU Dance Club):} 
  \begin{itemize}
    \item \textbf{Performed in the annual showcase}, demonstrating teamwork through intensive rehearsals.

    \item Served as a \textbf{Camp Counselor}, guiding and supporting new members to foster an inclusive and welcoming team environment.
  \end{itemize}
\end{itemize}

%----------------------------------------------------------------------------------------
%	AWARDS & HONORS
%----------------------------------------------------------------------------------------
\section{Awards and Honors}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
  \item \textbf{Honor Student:} 1st Semester of 2022 Academic Year
\end{itemize}



%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
%\vspace{-0.5cm}
%\noindent\rule{\textwidth}{0.4pt} 

\fontsize{10pt}{14pt}\selectfont
\noindent \textbf{Programming:} C (Advanced), Python (Advanced), C++ (Basic), Lua (Basic), \LaTeX \hspace{0.5cm} \\ [0.08cm]
\textbf{OS \& Architectures:} Linux, MacOS, ARMv8-A, AMD64  \\ [0.08cm]
\textbf{Framework \& Package:} PyTorch, OpenCV, Scikit-learn, C++ STL, POSIX Threads, OpenMP, CUDA \\ [0.08cm]
\textbf{Tools:} Git, GNU Make, GNU Plot, CMake, QEMU, GDB, Perf, Neovim, Tmux \\ [0.08cm]
\textbf{Language:} Chinese (Native), English (Fluent)

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
